manuscript_analysis_clean

### 2021-07-22 script/manuscript_clean_061021.Rmd
Update manuscript_clean_061021.Rmd

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  summarize(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```

>>>>

# Count N for each task
rt_trial %>%
  group_by(group, task) %>%
  filter(!is.na(reaction_time)) %>%
  summarize(n = length(unique(id))) %>%
  slice(match(c("lsl", "ssl", "vsl", "tsl"), task))
```
